\documentclass[a4paper,20pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{3pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{1pt}}
  }
}

\newcommand{\extraNote}[1]{
    \item\small{}
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\normalsize{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large\textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

    %HEADING
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{{\LARGE Adam Farrow}} & Email: \href{mailto:}{Adamfarrow1@gmail.com}\\
      \href%{INSERT PORTFOLIO URL HERE}{Portfolio: currently being developed}
      & Mobile:~~~407 341 4243 \\
      \href{https://github.com/AdamFarrow}{Github: ~~github.com/Adamfarrow1} \\
    \end{tabular*}
    
    %EDUCATION
    \section{Education}
        \resumeSubHeadingListStart
            \resumeSubheading{University of Central Florida}{Orlando, Florida}
                {Bachelors of Science - Computer Science}{August 2020 - Current}
            \resumeItemListStart
                \resumeItem{Cumulative GPA}{3.328}
            \resumeItemListEnd
        \resumeSubHeadingListEnd
    
    
    %SKILLS
    \section{Skills}
    	\resumeSubHeadingListStart
        	\resumeSubItem{Languages}{~~~~~~~~~~~~~~~~~~~~~~ Java, C, JavaScript, HTML, CSS, SCSS}
        	\vspace{-8pt}
        	\resumeSubItem{Frameworks/Tools}{~~~~~~~~~~~React.js, Node.js, MongoDB, Express, PHP, MySQL, Bootstrap, Firebase, Git, Jest}
        	\vspace{-8pt}
      \resumeSubHeadingListEnd
    
    
 
    
    %PROJECTS
    \section{Projects}
        \resumeSubHeadingListStart
            \resumeSubItem{Study Buddies}{ A MERN stack application that is used to connect with UCF students and study with them. The goal of this application is to find fellow UCF students who need a study partner
            \\Tech: React.js, MongoDB, Express, Bootstrap. (January 2023)}
            \resumeSubItem{Contact Manager}{ A full stack CRUD website using a LAMP stack. This website was a class project with a group full of 4 people. I was in charge of frontend and API.
            \\Tech: JavaScript, PHP, HTML, CSS. (February 2021)}
            \resumeSubItem{Messenger App}{Real-time messaging app with user authentication using React, Firebase, and Bootstrap. The purpose of this website was to learn React and Firebase.
            \\Tech: React, Firebase, JavaScript, HTML, CSS. (January 2023)}
            \resumeSubItem{Resume website}{A website hosted using GitHub pages that contains information about me. The purpose of the website is to give a visually appealing version of my resume.\\Tech: JavaScript, HTML, CSS. (September 2022)}
            \resumeSubItem{Infinite StairMaster}{Infinite StairMaster is a game where you try to see how high you can climb with intentionally tricky controls. This website was created at the ShellHacks hackathon 2022. I helped design and create a queue represented by a linked list to find out which next move our player should make. \\Tech: JavaScript, HTML, CSS. (September 2022)}
            \vspace{2pt}
        \resumeSubHeadingListEnd


           %EXPERIENCE
    \section{Experience and Leadership}
        \resumeSubHeadingListStart
            %Format similar to education
            \resumeSubheading{ShellHacks Hackathon}{Miami, Florida}{Competitor}{2022}
                \resumeItemListStart
                    \resumeItem{Team Leader/Presenter}{Different challenges were given from many different companies including Xbox, Microsoft, MITRE, and State Farm to name a few. Each project was presented and judges decided the winners of each project. Within the team we created, they designated me as the leader/presenter of the project.}
                \resumeItemListEnd
                 \resumeSubheading{UCF Hackathon}{Orlando, Florida}{Winner}{2023}
                \resumeItemListStart
                    \resumeItem{Team Leader/Presenter}{Winner of the UCF single day hackathon created by the University of Central Florida. We created a chrome extension that is used to help people with disabilities navigates websites. }
                \resumeItemListEnd
                \resumeSubheading{Football Captain}{Orlando, Florida}{Leader}{2016-2020}
                \resumeItemListStart
                    \resumeItem{Team Captain}{Captain of football team all 4 years of high school. As captain I got to make difficult decisions within a game that could impact the outcome.  }
                \resumeItemListEnd
                    
                    -
          \resumeSubHeadingListEnd
    
    
    
    %AWARDS
    \section{Other experience}
        \begin{description}[font=$\bullet$]
            \item {Cashier at Academy sports}
            \item {Math Tutoring at Beyond the classroom}
            \item {Truck loader at UPS}
            \item {Breader at PDQ}
            \item {High school Student government (made decision about school events)}
            
            % \item {Deans list spring 2021}
            % \item {UCF Hackathon winner}
        \end{description}
        
    %  %CLUBS
    % \section{Clubs/Extracurricular}
    %     \begin{description}[font=$\bullet$]
    %         \item {Knight Hacks club}
    %         \item {Brazilian Jiu Jitsu club}
    %     \end{description}
        
\end{document}
